Manuscript draft

### 2019-09-12 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

@@

Secondly, we emphasise that this study considers the relationship between productivity and climate on a coarse scale. Because of the nature of the ForC database, we were unable to access site-level MAT and MAP data for a number of sites, and lacked site-level data for other climate variables for all sites. As a result the climate data we used was primarily multi-year averages of annual climate measures accessed from global databases. While the quality of these data is high, we cannot expect that it captures detailed local variation in climate, and in particular will be unable to capture microclimate variation, which may have a strong influence on stand-level productivity. Although we find that MAT is the strongest predictor for climate, part of this effect may be a result of the higher-quality stand-level dataset available for MAT. With high-quality stand-level data for other climate variables we expect that their predictive strength would improve.

>>>>

The latitudinal gradient in FACF (Figs. 2-3) is driven primarily by temperature-related climate variables, with modification by moisture availability (Figs. 4-5). Because many climate variables co-vary across the latitudinal gradient, climatic drivers affect forest carbon flux on much shorter time scales than can be captured by annual climate summary variables, and both climatic conditions and C flux vary interannually around the long-term means, we would not expect any mean annual climate variable to explain variation in FACF. However, it remains informative to consider these relationships. We find that temperature-related climate variables explain the highest proportion of variability in productivity, and among these, $MAT$ is generally the best predictor--perhaps because site-specific MAT is recorded for the majority of sites in ForC, whereas other variables are extracted from a global database. .... The effects of temperature are modified by moisture availability, ...

@@
